Reproducible development environments with rix

### 2023-12-23 paper.qmd
tempfile -> tempdir

rix(r_ver = "4.3.1",
    r_pkgs = c("dplyr", "chronicler"),
    project_path = tempdir(),
    overwrite = TRUE,
    print = TRUE)
```

@@

```{r, eval = F}
rix(r_ver = "4.3.1",
    r_pkgs = c("dplyr", "chronicler", "AER@1.2-8"),
    system_pkgs = c("quarto", "git"),
    tex_pkgs = c(
          "amsmath",
          "framed",
          "fvextra",
          "environ",
          "fontawesome5",
          "orcidlink",
          "pdfcol",
          "tcolorbox",
          "tikzfill"
    ),
    git_pkgs = list(
                 list(package_name = "rix",
                   repo_url = "https://github.com/b-rodrigues/rix/",
                   branch_name = "master",
                   commit = "ea92a88ecdfc2d74bdf1dde3e441d008521b1756"),
                 list(package_name = "fusen",
                   repo_url = "https://github.com/ThinkR-open/fusen",
                   branch_name = "main",
                   commit = "d617172447d2947efb20ad6a4463742b8a5d79dc")
    ),
    ide = "rstudio",
    project_path = tempfile(),
    overwrite = TRUE)
```

@@

rix(r_ver = "4.3.1",
    r_pkgs = c("dplyr", "chronicler", "AER@1.2-8"),
    system_pkgs = c("quarto", "git"),
    tex_pkgs = c(
          "amsmath",
          "framed",
          "fvextra",
          "environ",
          "fontawesome5",
          "orcidlink",
          "pdfcol",
          "tcolorbox",
          "tikzfill"
    ),
    git_pkgs = list(
                 list(package_name = "rix",
                   repo_url = "https://github.com/b-rodrigues/rix/",
                   branch_name = "master",
                   commit = "ea92a88ecdfc2d74bdf1dde3e441d008521b1756"),
                 list(package_name = "fusen",
                   repo_url = "https://github.com/ThinkR-open/fusen",
                   branch_name = "main",
                   commit = "d617172447d2947efb20ad6a4463742b8a5d79dc")
    ),
    ide = "rstudio",
    project_path = tempfile(),
    print = TRUE)
```

>>>>

rix(r_ver = "4.3.1",
    r_pkgs = c("dplyr", "chronicler"),
    project_path = ".",
    overwrite = TRUE,
    print = TRUE)
```

@@

```{r, eval = F}
rix(r_ver = "4.3.1",
    r_pkgs = c("dplyr", "chronicler", "AER@1.2-8"),
    system_pkgs = c("quarto", "git"),
    tex_pkgs = c(
          "amsmath",
          "framed",
          "fvextra",
          "environ",
          "fontawesome5",
          "orcidlink",
          "pdfcol",
          "tcolorbox",
          "tikzfill"
    ),
    git_pkgs = list(
                 list(package_name = "rix",
                   repo_url = "https://github.com/b-rodrigues/rix/",
                   branch_name = "master",
                   commit = "ea92a88ecdfc2d74bdf1dde3e441d008521b1756"),
                 list(package_name = "fusen",
                   repo_url = "https://github.com/ThinkR-open/fusen",
                   branch_name = "main",
                   commit = "d617172447d2947efb20ad6a4463742b8a5d79dc")
    ),
    ide = "rstudio",
    project_path = ".",
    overwrite = TRUE)
```

@@

rix(r_ver = "4.3.1",
    r_pkgs = c("dplyr", "chronicler", "AER@1.2-8"),
    system_pkgs = c("quarto", "git"),
    tex_pkgs = c(
          "amsmath",
          "framed",
          "fvextra",
          "environ",
          "fontawesome5",
          "orcidlink",
          "pdfcol",
          "tcolorbox",
          "tikzfill"
    ),
    git_pkgs = list(
                 list(package_name = "rix",
                   repo_url = "https://github.com/b-rodrigues/rix/",
                   branch_name = "master",
                   commit = "ea92a88ecdfc2d74bdf1dde3e441d008521b1756"),
                 list(package_name = "fusen",
                   repo_url = "https://github.com/ThinkR-open/fusen",
                   branch_name = "main",
                   commit = "d617172447d2947efb20ad6a4463742b8a5d79dc")
    ),
    ide = "rstudio",
    project_path = tempdir(),
    overwrite = TRUE,
    print = TRUE)
```
